---
title: "easyformatr"
author: "Brandon Taylor"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{easyformatr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Import the package. We will also make heavy usage of magrittr for chaining, dplyr for filtering, and knitr for printing.

```{r, message = FALSE}
library(easyformatr)
library(magrittr)
library(dplyr)
library(knitr)
```

# Base Components
Let's see what kind of componenets we can use in our time formats. This can be done by filtering the format info table.

## Times

```{r}
filter_info(type == "time" & component == "base")
```

## Numbers

```{r}
filter_info(type == "number" & component == "base")
```

Each of these base components can be used in a formats.

```{r}
easy_format(year, month, day, integer, octal, double)
```

# Mutant documentation
Each base component can be modified in special ways. 

## Time 
Each time base can be modified in different ways. Let's look at ways to modify second:

```{r}
filter_info(type == "time" & component == "mutant" & base == "second")
```

Along the top, you can see the names of flags and options. Flags change logical variables, and options change numeric variables.

## Numbers
It is slightly easier to see modifiers for numbers because there is a fixed set.

### Flags

```{r}
filter_info(type == "number" & component == "flag")
```

### Options

```{r}
filter_info(type == "number" & component == "option")
```

# Transformations

To transform a base into a mutant, you must use a flag or option function. These functions take two arguments. The first is an object to modify:

```{r}
easy_format(second %>% decimal)
```

or a list of objects to modify:
```{r}
easy_format(list(integer, 
                 double) %>% 
              always_decimal)
```

or even a nested list of objects to modify

```{r}
easy_format(list(month, 
                 list(day,
                      minute) ) %>% 
            roman)
```

In the case of times, flags or options that aren't relevant to a particular base (that is, aren't listed in the mutant table for a particular base) have no effect. Flags and options always have an effect on numbers.

```{r}
easy_format(second %>% roman) ==
  easy_format(second)
```

## The second argument
The second argument of a transformation is what to change the value to.

### Flags

For flags, the second argument defaults to true.
 
```{r}
easy_format(second %>% decimal) == 
  easy_format(second %>% decimal(TRUE) )
```

Flags can be undone by resetting the value to NA.

```{r}
easy_format(second %>% 
              decimal %>% 
              decimal(NA) ) ==
  easy_format(second)
```

### Options

For options, this second value defaults to NA. So options will have no effect if no number is chosen.

```{r}
easy_format(double %>% before_decimal) == 
  easy_format(double)
```

Options can be turned of by resetting them to NA

```{r}
easy_format(double %>% before_decimal(3) %>% before_decimal) == 
  easy_format(double)
```

## Errors
For times, it is possible to specify a mutant that has no corresponding code. For example,
```{r, error = TRUE}
easy_format(second %>%
              decimal %>%
              digits(1) ) 
```

# Strings

Easy format leaves strings unchanged. However, percentage signs will be doubled.
```{r}
easy_format("We are the 99%")
```

This only happens once.
```{r}
easy_format(easy_format("We are the 99%") )
```

Modifications also leave strings unchanged.

```{r}
easy_format(roman("I am Spartacus"))
```

There is an optional sep argument that defaults to `""`, but can be changed.

```{r}
easy_format("We", "are", "the 99%", sep = " ")
```

# More Info
For more information, codes can be looked up in the `?strptime` and the `?sprintf` documentation. Note that many formats are possible to build but will not work when used.

